\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-14 paper.tex
Tech
done
Slight mods
Update abstract

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the three major use-cases associated with course scheduling---direct, exploratory, and peer-guided search---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

@@

% Bibtex commands go here
\bibliographystyle{ieeetr}
\bibliography{bibliography}

@@

\clearpage
\section*{Appendix}

>>>>

In this paper I present Skedge, a web application made for students to comfortably and effectively engage with the University’s course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS), and boasts strong student adoption and retention rates despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and meet real-world needs, \textbf{b)} the three major use-cases associated with course scheduling---direct search, exploratory search, and peer-guided search---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

@@

% Bibtex commands go here

\begin{spacing}{1.1}

\bibliographystyle{ieeetr}
\bibliography{bibliography}

\end{spacing}

@@
